LAGOS lake depth

### 2019-12-28 figures/00_maps.Rmd
create figures pipeline

```{r 11_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(maxdepth_class = smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, Inf)))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
hu4_focal     <- st_crop(st_transform(
  lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)), 
  study_bbox)

>>>>

```{r 00_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
dt            <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(maxdepth_class = smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, Inf)))
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
hu4_focal     <- st_crop(st_transform(
  lwgeom::st_make_valid(hu4_focal), st_crs(study_bbox)), 
  study_bbox)
